---
title: "Google Sheets"
author: "Claire"
date: "July 7, 2015"
output: html_document
---

This is a lab to practice with Google Sheets and the `googlesheets` package.

1. If you haven't already go to the class Google Sheet and add your information:  https://docs.google.com/spreadsheets/d/1FJ_k8krqoO5E7L5vjEMjB3vMoMcBRmAzxQ5tkJodT34/

2. Use the `googlesheets` package to read in the data like we discussed in class. 

Best practice: save the date so that you have a record. Google keeps all of the versions
By default, reads until the last line of text in the google sheet.

```{r}
sheets_url = "https://docs.google.com/spreadsheets/d/1FJ_k8krqoO5E7L5vjEMjB3vMoMcBRmAzxQ5tkJodT34/pubhtml"

gsurl1 = gs_url(sheets_url)
dat = gs_read(gsurl1)
date_downloaded=date()

dat
```

3. Look at the arguments for `cell_rows`, `cell_limits` and `cell_cols`. 

Readme here: https://github.com/jennybc/googlesheets

Essentially these allow you to restrict the range of cells imported.

cell_limits(ul = c(ROW_MIN, COL_MIN), lr = c(ROW_MAX, COL_MAX))


4. Try reading in just the first two columns. 


```{r}
dat2 = gs_read(gsurl1, range = cell_cols(1:2))

dat2

dat3= gs_read(gsurl1, range = cell_limits(ul = c(2, 2), lr = c(5,6 )))

dat3
```
